{\normalsize Seminar: Formal Specification} \\[1ex] Security of Multithreaded Programs by Compilation\cite{Barthe07}

### 2012-02-01 paper/paper.tex
use package hyperref instead of url
some more corrections

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}
\usepackage{todonotes}
\usepackage{mathpartir}
\usepackage{nameref}
\usepackage{url}

@@

\begin{definition}
The junction points are computed by a function $jun: \mathcal{P} \rightarrow \mathcal{P}$. It is defined
on all junction points $[c]^n$ in the source program and its domain is $jun(n) = max \{i\ |\ i \in tregion(n)\} + 1$.
\end{definition}

@@

The first rule \textsc{L-Cond} from Figure \ref{fig:typing-rules-if} says that if we branch on a low
guard, everything depends on the security level of $c$ and $c'$. The rule \textsc{H-Cond} covers the
case where we have a high guard, in this case the control dependence region has to be marked
high. The rule \textsc{Top-H-Cond} is the interesting one. Because of the preceding rules we can not
be part of branch with a low guard, therefore we are in the outermost high branch. The premise
$E' = lift_H(E, sregion(n))$ reads as: For all labels in the control dependence region $E$ is
defined as $E'(n) = H \sqcup E(n)$ and $E'(n) = E(n)$ for all other labels.

@@

Where $T$ and $T'$ are traces of the execution of a program. $m$ and $m'$ are initial configurations.
Let $T(L) = [M_0(L), M_1(L), \dots]$ be the list of values at location $L$ in the trace $T$. Then
$T \approx_\zeta T'$ holds if the values of $T(L)$ and $T'(L)$ are pairwise indistinguishable. Since
it is allowed that one sequence is a prefix of the other, there is no need to proof termination, but
external timing attacks are possible.

>>>>

\usepackage{graphicx}
\usepackage{multicol}
\usepackage{amsbsy,amscd,amsfonts,amssymb,amstext,amsmath,latexsym,theorem}
\usepackage{todonotes}
\usepackage{mathpartir}
\usepackage{nameref}
\usepackage{hyperref}

@@

\begin{definition}
The junction points are computed by a function $jun: \mathcal{P} \rightarrow \mathcal{P}$. This function is defined
on all junction points $[c]^n$ in the source program and its domain is $jun(n) = max \{i\ |\ i \in tregion(n)\} + 1$.
\end{definition}

@@

The first rule \textsc{L-Cond} from Figure \ref{fig:typing-rules-if} says that if we branch on a low
guard, then everything depends on the security level of $c$ and $c'$. The rule \textsc{H-Cond} covers the
case where we have a high guard, in this case the control dependence region has to be marked
high. The rule \textsc{Top-H-Cond} is the interesting one. Because of the preceding rules we can not
be part of branch with a low guard, therefore we are in the outermost high branch. The premise
$E' = lift_H(E, sregion(n))$ reads as: For all labels in the control dependence region $E$ is
defined as $E'(n) = H \sqcup E(n)$ and $E'(n) = E(n)$ for all other labels.

@@

where $T$ and $T'$ are traces of the execution of a program. $m$ and $m'$ are initial configurations.
Let $T(L) = [M_0(L), M_1(L), \dots]$ be the list of values at location $L$ in the trace $T$.
$T \approx_\zeta T'$ holds if the values of $T(L)$ and $T'(L)$ are pairwise indistinguishable. Since
it is allowed that one sequence is a prefix of the other, there is no need to proof termination, but
external timing attacks are possible.
